Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-09-14 fully-abstract-comp/technical-report.tex
Add a note.

In other words, we needed a system-wide guarantee to be able to put some trust in linear capabilities from untrusted a source we do not trust.
\end{itemize}

>>>>

In other words, we needed a system-wide guarantee to be able to put some trust in linear capabilities from an untrusted source.

Note that it would be good if malloc provided a way to initially obtain a linear capability in this model.
Otherwise, there would never be any linear capabilities other than stack pointers, which seems a waste.
\end{itemize}
